\documentclass[a4paper]{article}

\usepackage[english]{babel}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage[colorinlistoftodos]{todonotes}

\title{Evaluating \& Predicting the Reliability of Redditors}

\author{Kashev Dalmia - \texttt{dalmia3@illinois.edu} \\
        Ryan Freedman - \texttt{rtfreed2@illinois.edu} \\
        Terence Nip - \texttt{nip2@illinois.edu}
        }

\date{\today}

\begin{document}
\maketitle

\begin{abstract}

Reddit is emerging as an increasingly popular, and thus important, social
network. Reddit is based almost entirely on `uncurated' content. Users post
about what is interesting to them in portions of the website called subreddits.
In general, subreddits are organized by topic, so it becomes relatively easy to
find content based on ones interests. Once content is posted, users can up-vote
or down-vote content and comments on that content, and these scores are
aggregated so the `best' content becomes easier to find.

Reddit users, or Redditors, can be extremely engaged and reliable, and therefore
useful as sensors. In this paper, we develop a method of determining if Reddit
users are reliable based on their post and comment history, as well as the
reaction of the community to their activity. Furthermore, we use this Redditor
data to create an accurate predictor of future Redditor activity. Users
exhibiting signs of future reliable sources can then be encouraged on the
behaviors that turn them into reliable users. Similarly, users who are not
reliable can be discouraged from posting.

\end{abstract}


\end{document}
