Reddit, the self-proclaimed ``Frontpage of the Internet'', is a website
containing entirely user-contributed, uncurated content organized by topic. Over
the past few years, Reddit has gained prominence within popular media channels
for various reasons, all surrounding the content submitted by Reddit users, or
Redditors.

Redditors can be extremely engaged and reliable, and therefore useful as
sensors. In this paper, we propose a method of determining if Redditors are
reliable based on their post and comment history, as well as the reaction of the
community to their activity. Furthermore, the resulting analysis can be used to
create a predictor of future Redditor activity. For example, this would allow
for the creation of nudges to encourage users who demonstrate potential
dependability to turn them into actual, reliable users - and conversely,
discourage unreliable users from posting on Reddit, increasing the net
dependability of the site.

\subsection{Why Reddit?}
\label{sub:why_reddit}

Reddit is quickly becoming a larger and larger social network, and much of its
potential remains untapped. It is unique among social networks for a few
reasons, the combination of which make it attractive for study and use as a
sensor network.

Though more things can be posted, Twitter is primarily used for text. Instagram
is for photos, and Vine is for videos. Reddit, however, is extremely content
agnostic; Users post photos, links, videos, and text, relating to a variety of
topics. Twitter caps users at 140 characters, Reddit does not. Facebook is
mostly private content, Reddit is largely public. Reddit also comes with the
built in benefit of content being organized by subject matter, into various
`Subreddits'. In this way, many positive user behaviors are already encouraged,
like posting content in the proper Subreddit.

% subsection why_reddit (end)

\subsection{Finding Reliable Users}
\label{sub:finding_reliable_users}

There are some issues with Reddit that are less present in social networks like
Twitter. For instance, Twitter has verified accounts, and if the verified
account \texttt{@cnn} tweets something, one can be relatively sure it is
researched and vetted information which is likely to be correct. Reddit has no
such mechanism, nor accounts for brands or news organizations. Moreover, many
Reddit users are completely anonymous and could potentially have multiple
accounts, which can cause rise to all sorts of poor behavior. Thus, determining
the reliability of users is a challenge not just for most users as it is for
Twitter, but for all users.

% subsection creating_good_users (end)
